---
title: ""
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'design.html'))})
 
css: zme_style.css
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:MidnightBlue;
    	cursor: url('/Users/zoeervolino/Documents/zoe/zoe/cursor.cur'), default;
}
</style>

<a href="https://zoervolino.github.io/zoe/">
<font size=80>
<h1>Zoe M`r emo::ji("dizzy")`rales Ervolino</h1>
</font>
</a>

<a2>
<small>
<small><small><a href="about.html"><i>ABOUT</a>  </i></small></small>
<b><b><small><small><a href="design.html"><i>ART</a>  </i></small></small></b></b> 
<small><small><a href="contact.html"><i>CONTACT</a>  </i></small></small> 
<small><small><a href="https://tinyletter.com/unfriendlybrujita/archive"><i>ARCHIVE</a>  </i></small></small>
</small>
</a2>  
<br>
<a1><b>Zoe Morales Ervolino</a1></b> <small><small>does art stuff sometimes.
<br>
<br>
If you like, <a href="https://zoervolino.github.io/cartagena/">enjoy some of the photographs</a> she took during a recent trip to Cartagena, Colombia and the nearby cities of Barranquilla and San Andres. 
<br>
<br>
You can also take a look at the acrylic and oil paintings she has done. 
<br>
<br>
<hr>
<br>
<font size=60>
<b><a2>tan boba</a2></b>
</font>
<br>
<a2>oléo sobre lienzo</a2>
```{r image3, echo=FALSE, out.width="70%", fig.align='center'}
a <- "IMG_0113.JPG"
knitr::include_graphics(a)
```
<br>
<br>
<b><a2>auto-retrato rojito</a2></b><br>
<a2>acrílico sobre papel</a2>
```{r image4, echo=FALSE, out.width="70%", fig.align='center'}
a <- "IMG_9513.JPG"
knitr::include_graphics(a)
```
<br>
<br>
<b><a2>carita</a2></b><br>
<a2>acrílico sobre papel</a2>
```{r image5, echo=FALSE, out.width="70%", fig.align='center'}
a <- "IMG_0107.JPG"
knitr::include_graphics(a)
```
<br>
<br>
<b><a2>reflexión desnuda</a2></b>
<br>
<a2>oléo sobre lienzo</a2>
```{r image6, echo=FALSE, out.width="70%", fig.align='center'}
a <- "IMG_1970.JPG"
knitr::include_graphics(a)
```
<br>
<br>
<b><a2>la maldición del vientre</a2></b>
<br>
<a2>acrílico sobre papel</a2>
```{r image7, echo=FALSE, out.width="70%", fig.align='center'}
a <- "IMG_0105.JPG"
knitr::include_graphics(a)
```
<br>
</small></small>
<br>
<br>
<b><a2>huevitos abstractos</a2></b>
<br>
<a2>oléo sobre lienzo</a2>
```{r image8, echo=FALSE, out.width="70%", fig.align='center'}
a <- "IMG_0101.JPG"
knitr::include_graphics(a)
```
<br>
<br>
<b><a2>la niña verde</a2></b>
<br>
<a2>acrílico sobre papel</a2>
```{r image9, echo=FALSE, out.width="70%", fig.align='center'}
a <- "IMG_0100.JPG"
knitr::include_graphics(a)
```
<br>
</small></small>
<br>
<hr>
<br>
<small>
<small>
<center>
<i><a href="#top">back to top of page</a>
</center>
</i>
</small>
</small>
</br>