---
title: ""
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'design.html'))})
 
css: zme_style.css
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:PowderBlue;
    	cursor: url('/Users/zoeervolino/Documents/zoe/cursor.cur'), default;
}
</style>

<a href="https://zoervolino.github.io/zoe/"><font size=80>
<h1 style=>
ZOE `r emo::ji("dizzy")` ERVOLINO
</h1>
</font></a>

<small><small><a href="design.html"><i>ART</a>  </i></small></small> 
<small><small><a href="about.html"><i>ABOUT</a>  </i></small> 
<small><a href="contact.html"><i>CONTACT</a>  </i></small> 
<small><a href="https://tinyletter.com/unfriendlybrujita/archive"><i>ARCHIVE</a>  </i></small> 

Zoe Morales Ervolino <small><small>does art stuff sometimes.

If you like, <a href="https://zoervolino.github.io/cartagena/">enjoy some of photographs</a> she took during a recent trip to Cartagena, Colombia and the nearby cities of Barranquilla and San Andres. 

You can also peruse the acrylic and oil studies she has done over the past few years. 


<a2>tan boba</a2>
```{r image3, echo=FALSE, out.width="60%", fig.align='center'}
a <- "IMG_0113.JPG"
knitr::include_graphics(a)
```
<a2>auto-retrato rojito</a2>
```{r image4, echo=FALSE, out.width="60%", fig.align='center'}
a <- "IMG_9513.JPG"
knitr::include_graphics(a)
```

<a2>carita</a2>
```{r image5, echo=FALSE, out.width="60%", fig.align='center'}
a <- "IMG_0107.JPG"
knitr::include_graphics(a)
```

<a2>reflexión desnuda</a2>
```{r image6, echo=FALSE, out.width="60%", fig.align='center'}
a <- "IMG_1970.JPG"
knitr::include_graphics(a)
```

<a2>la maldición del vientre</a2>
```{r image7, echo=FALSE, out.width="60%", fig.align='center'}
a <- "IMG_0105.JPG"
knitr::include_graphics(a)
```
</small></small>