---
title: ""
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

self_contained: false

css: zme_style.css
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:PowderBlue;
    	cursor: url('/Users/zoeervolino/Documents/zoe/cursor.cur'), default;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(embedr)
library(vembedr)
library(tinytex)
library(emo)
library(rmdprotectr)
library(rmarkdown)
```

<a href="https://zoervolino.github.io/zoe/">
<font size=80>
<h1 style=>
ZOE `r emo::ji("dizzy")` ERVOLINO
</h1>
</font>
</a>

<small><a href="contact.html"><i>Contact</i></a></small>

```{r image1, echo=FALSE, out.width="100%", fig.align='center'}

mascara <- "/Users/zoeervolino/Documents/zoe/bookmark_zme.jpg"
knitr::include_graphics(mascara)

```

Zoe Morales Ervolino <a1>is a born-and-bred New Yorker and recent Yale graduate where she earned a dual-degree in American Studies and History. Somewhere along the way she developed a penchant for R. Perhaps more surprisingly, this website is the result.</a1> 

```{r image2, echo=FALSE, out.width="40%", fig.align='center'}

zoe <- "/Users/zoeervolino/Documents/zoe/IMG_1710.JPG"
knitr::include_graphics(zoe)

```

<h2>**❣ listen ❣**</h2>

el laberinto 

```{r lab, echo=FALSE, eval=TRUE}
lab <- "/Volumes/NO NAME/zoe/laberinto.mp3"
embed_audio(lab, attribute = c("controls"), type = "mpeg")
```


<h3>**❣ enjoy ❣**</h3>

el viaje

```{r viaje, echo=FALSE, fig.align='center'}
viaje <- "/Volumes/NO NAME/zoe/ft.mp4"
embed_video(
  viaje, 
  type = "mp4", 
  height = "90%", 
  attribute = "controls",
    thumbnail = "/Volumes/NO NAME/zoe/viaje.jpeg",
)
```

<h6>❣ watch ❣</h6>

triangulations

<div style="padding:56.25% 0 0 0;position:relative;"><iframe src="https://player.vimeo.com/video/463677663" style="position:absolute;top:0;left:0;width:100%;height:100%;" frameborder="0" allow="autoplay; fullscreen; picture-in-picture" allowfullscreen></iframe></div><script src="https://player.vimeo.com/api/player.js"></script>
<p><a href="https://vimeo.com/463677663">Triangulations</a> by <a href="https://vimeo.com/user124123052">Zoe Ervolino</a> on <a href="https://vimeo.com">Vimeo</a>.</p>

<h4>**❣ peruse ❣**</h4>

auto-retrato

```{r image4, echo=FALSE, out.width="50%", fig.align='center'}

zoe2 <- "/Volumes/NO NAME/zoe/FullSizeRender.jpeg"
knitr::include_graphics(zoe2)

```


<p><h7>❣ thanks for stopping by ❣</h7></p>

<a2><form style="border:1px solid #ccc;padding:3px;text-align:center;" action="https://tinyletter.com/unfriendlybrujita" method="post" target="popupwindow" onsubmit="window.open('https://tinyletter.com/unfriendlybrujita', 'popupwindow', 'scrollbars=yes,width=800,height=600');return true"><p><label for="tlemail">keep in touch</label></p><p><input type="text" style="width:140px" name="email" id="tlemail" /></p><input type="hidden" value="1" name="embed"/><input type="submit" value="`r emo::ji("star")` subscribe `r emo::ji("star")`" /><p><a href="https://tinyletter.com" target="_blank"></a></p></form></a2>
        
    
