---
title: ""
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
 
css: zme_style.css
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:PowderBlue;
    	cursor: url('/Users/zoeervolino/Documents/zoe/cursor.cur'), default;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(embedr)
library(tinytex)
library(emo)
library(rmdprotectr)
```

<font size=80>
<h1 style=>
ZOE `r emo::ji("dizzy")` ERVOLINO
</h1>
</font>

```{r image1, echo=FALSE, out.width="100%", fig.align='center'}

mascara <- "/Users/zoeervolino/Documents/zoe/bookmark_zme.jpg"
knitr::include_graphics(mascara)

```

<font size=60>Zoe Morales Ervolino </font>is a born-and-bred New Yorker and recent Yale graduate where she earned a dual-degree in American Studies and History. Somewhere along the way she developed a penchant for R. Perhaps more surprisingly, this website is the result. 

```{r image2, echo=FALSE, out.width="40%", fig.align='center'}

zoe <- "/Users/zoeervolino/Documents/zoe/IMG_1710.JPG"
knitr::include_graphics(zoe)

```

<h2>**❣ listen ❣**</h2>

el laberinto 


```{r lab, echo=FALSE, eval=TRUE}
lab <- "/Volumes/NO NAME/zoe/laberinto.mp3"
embed_audio(lab, attribute = c("controls"), type = "mpeg")
```


<h3>**❣ watch ❣**</h3>

el viaje

```{r viaje, echo=FALSE, fig.align='center'}
viaje <- "/Volumes/NO NAME/zoe/ft.mp4"
embed_video(
  viaje, 
  type = "mp4", 
  height = "90%", 
  attribute = "controls",
    thumbnail = "/Volumes/NO NAME/zoe/viaje.jpeg",
)
```

<h4>**❣ peruse ❣**</h4>

auto-retrato

```{r image4, echo=FALSE, out.width="50%", fig.align='center'}

zoe2 <- "/Volumes/NO NAME/zoe/FullSizeRender.jpeg"
knitr::include_graphics(zoe2)

```

<h5><font size=80>**❣ thanks for stopping by ❣**</font><h/5>
