---
title: ""
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

self_contained: false

css: zme_style.css
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
    background-color:PowderBlue;
    	cursor: url('/Users/zoeervolino/Documents/zoe/cursor.cur'), default;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(embedr)
library(vembedr)
library(tinytex)
library(emo)
library(rmdprotectr)
library(rmarkdown)
```
<head>
<a href="https://zoervolino.github.io/zoe/">
<font size=80>
<h1>Zoe M`r emo::ji("dizzy")`rales Ervolino</h1>
</font>
</a>
<b>
<a2>
<small>
<small><small><a href="about.html"><i>ABOUT</a>  </i></small></small>
<small><small><a href="design.html"><i>ART</a>  </i></small></small> 
<small><small><a href="contact.html"><i>CONTACT</a>  </i></small></small> 
<small><small><a href="https://tinyletter.com/unfriendlybrujita/archive"><i>ARCHIVE</a>  </i></small></small>
</small>
</a2>  
</b>
</head>
<a name="top"></a>
<body>
<a href="https://zoervolino.github.io/zoe/design.html">
```{r image1, echo=FALSE, out.width="100%", fig.align='center'}
a <- "/Users/zoeervolino/Documents/zoe/bookmark_zme.jpg"
knitr::include_graphics(a)
```
</a>

<a1><b>Zoe Morales Ervolino</a1></b> <small>is a born-and-bred New Yorker and recent Yale graduate. Somewhere along the way she developed a penchant for R. Perhaps more surprisingly, this website is the result.</small>

```{r image2, echo=FALSE, out.width="40%", fig.align='center'}

zoe <- "/Users/zoeervolino/Documents/zoe/IMG_1710.JPG"
knitr::include_graphics(zoe)

```
<br>
<hr>
<br>
<center>
<h3>**❣ enjoy ❣**</h3>
</center>
<center>
el viaje
</center>
```{r viaje, echo=FALSE, fig.align='center'}
viaje <- "/Volumes/NO NAME/zoe/ft.mp4"
embed_video(
  viaje, 
  type = "mp4", 
  height = "90%", 
  attribute = "controls",
    thumbnail = "/Volumes/NO NAME/zoe/viaje.jpeg",
)
```
<br>
<hr>
<br>
<center>
<h6>❣ watch ❣</h6>
</center>
<center>
view triangulations <a href="https://youtu.be/rf0VjGLtb3g?t=253"><b>here</b></a>
</center>
```{r triangulations, echo=FALSE, fig.align='center', out.width="50%"}
##embed_vimeo("463677663") %>%
  ##use_bs_responsive()
```
<br>
<hr>
<br>
<center>
<h4>**❣ peruse ❣**</h4>
</center>
<center>
auto-retrato
</center>
```{r image4, echo=FALSE, out.width="50%", fig.align='center'}

zoe2 <- "/Volumes/NO NAME/zoe/FullSizeRender.jpeg"
knitr::include_graphics(zoe2)

```
<br>
<hr>
<br>
<center>
<h2>**❣ listen ❣**</h2>
</center>
<center>
el laberinto 
</center>
<center>
```{r lab, echo=FALSE, eval=TRUE}
lab <- "/Volumes/NO NAME/zoe/laberinto.mp3"
embed_audio(lab, attribute = c("controls"), type = "mpeg")
```
</center>
<center>
<small>further sonic pleasure <a href="https://soundcloud.com/zoe-ervolino"><b>here</a></b>
</small>
</center>
<br>
<hr>
<br>
<center>
<p><h7>❣ thanks for stopping by ❣</h7></p>
</center>
<a2><form style="border:2px solid #3cc;padding:3px;text-align:center;" action="https://tinyletter.com/unfriendlybrujita" method="post" target="popupwindow" onsubmit="window.open('https://tinyletter.com/unfriendlybrujita', 'popupwindow', 'scrollbars=yes,width=800,height=600');return true"><p><label for="tlemail">keep in touch</label></p><p><input type="text" style="width:140px" name="email" id="tlemail" /></p><input type="hidden" value="1" name="embed"/><input type="submit" value="`r emo::ji("star")` subscribe `r emo::ji("star")`" /><p><a href="https://tinyletter.com" target="_blank"></a></p></form></a2>
</body>
<br>
<hr>
<br>
<small>
<small>
<center>
<i><a href="#top">back to top of page</a>
</center>
</i>
</small>
</small>
</br>

